\section{Problem}

Attributes have proved to be a very useful way to perform
source code annotations. However to increase their use some
issues need to be better clarified.

\subsection{Handling unknown attribute namespaces}

During the committee meeting at Kona it was pointed out that \emph{``We don't
have a requirement that implementations ignore attribute namespaces that they
do not understand. So my users hide attributes behind macros''}. This is something
that needs to be clarified in order to avoid attributes being hidden by macros.

Currently, the standard states in 7.6.1/3 that \emph{``The use of an
attribute-scoped-token is conditionally-supported, with implementation-defined
behavior''}. Making namespaced attributes conditionally supported means that
they will not be understood by implementations that do not cover that namespace.

\subsection{Non standard unqualified attributes}

Currently, the standard states in 7.6.1/5 that \emph{``For an attribute-token
not specified in this International Standard, the behavior is
implementation-defined''}. However this wording (combined with namespaces being
conditionally supported) may lead to implementations to add non-standard attributes
as extensions.

In general, the current status quo favors the fact that different implementations
pollute the global namespace with non-standard attributes in different ways, making
very difficult standardization of attributes in future versions.

It has been pointed out that being \emph{implementation-defined} allows a compiler
to support in a previous mode an attribute added in a newer version. For example
supporting in C++11 mode an attribute that was added for C++14. While, this is an
interesting use, it can be done as a non-conforming extension.
